Articles_Plots

### 2022-04-09 Articles.Rmd
update articles file with resolution

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "SMSE_MI_LR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggexport(filename = "SMSE_MI_LR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
```

>>>>

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "SMSE_MI_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggexport(filename = "SMSE_MI_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 16)
```
